BurgerTown Presents: Open Adcess

### 2017-05-15 future-work.tex
revolution description

\subsection{Ad-Free Edition}
For those who are physically able and enthusiastic about being part of
something big, the ACM offers ad free papers in exchange for manual labor at
your local ACM work dungeon.
This labor involves turning a very large crank around a pivot point in the
floor.
The crank is attached to a magnet spinning in a metal coil to generate the
necessary electricity required to power our servers.
However, all of this electricity is currently used to power electric lumbar
support for OSHA employees in case of a surprise inspection in exchange for
their continued appreciation of the safe practices within our work dungeons.
Two months of full-time service provides access to five ad-free papers.
Professors may opt to have their graduate students turn the crank in their name
to count towards their service.

@@

\subsection{ACM Seizes Means of Production}
The ACM has successfully seized the means of production.
The mills that are now used to power our servers were previously used to grind
healing crystals into a fine powder.
This powder was slipped into the coffee of unsuspecting CEOs where it worked to
slowly make them more susceptible to the messages of the ACM.
After years of crystal ingestion, the CEOs of the world's largest companies
ceded control of their companies to the ACM.
We are happy to announce that there currently exist no companies other than the
ACM.

>>>>

\subsection{Ad-Free Edition}
oFor those who are physically able and enthusiastic about being part of
something big, the ACM offers ad free papers in exchange for manual labor at
your local ACM work dungeon. 
This labor involves turning a very large crank around a pivot point in the
floor.
The crank is attached to a magnet spinning in a metal coil to generate the
necessary electricity required to power our servers.
However, all of this electricity is currently used to power electric lumbar
support for OSHA employees in case of a surprise inspection in exchange for
their continued appreciation of the safe practices within our work dungeons.
TTwo months of full-time service provides access to five ad-free papers.
Professors may opt to have their graduate students turn the crank in their name
to count towards their service.

@@

\subsection{ACM Seizes Means of Production}
The ACM has successfully seized the means of production. While a soviet of 
technicians along the lines of what Veblen had proposed was discussed in these 
pages in the fine print of ads for a supersoda that only engineers in the 
``lifehacking" crowd could possibly have read, the revolution was not thanks
to the engineers---who, even when fully aware that the ``industrial dictatorship
of the captain of finance" was ``held on sufferance of the engineers" and ``liable
to at any time be discontinued at their discretion, as a matter of convenience" were
unable to commit to revolution.
Instead, the work of revolution was done through ``the long march through the institutions,"
as Rudi Dutschke put it. In short, we had the baristas do it. They understand solidarity.

The mills that are now used to power our servers were previously used to grind
healing crystals into a fine powder. 
This powder was slipped into the coffee of unsuspecting CEOs where it worked to
slowly make them more susceptible to the messages of the ACM---to, as Veblen put it,
``understand that the whole fabric of credit and corporation finance is a tissue of make-believe"
and that, post-revolution, the same technicians and engineers could manage production, organized
around the common interest and not the interests of absentee owners.
After years of crystal ingestion, the CEOs of the world's largest companies 
ceded control of their companies to the ACM. (Except the Virgos: we had to kill them.)
We are happy to announce that there currently exist no companies other than the
ACM.
